---
title: "Assignment 1"
author: "Sean Bradford"
date: "June 29, 2022"
output:
  html_document:
    df_print: paged
  word_document: default
subtitle: 'Description: This assignment involved installing/configuring R and dependent
  libraries, running commands against Carseats dataset, and evaluating results of
  plotting Sales against Price to determine their correlation.'
---

1.
Installed ISLR library and called library(ISLR).

install.packages('ISLR')

library(ISLR)


2.
```{r}
# Call ISLR library
library(ISLR)
# Print summary of Carseats
summary(Carseats)
```
```{r}
# Determine number of rows in Carseats
nrow(Carseats)
```
The dataset contains 400 rows.

3.
The max value for advertising is 29.000

4.
```{r}
# Calculate IQR for Price
IQR(Carseats$Price)
```
IQR for Price is 31

5.
```{r}
# Plot Sales vs. Price
plot(Carseats$Price,Carseats$Sales)
```

Sales is slightly correlated with price. As price increases, sales decreases. 
```{r}
# Calculate correlation between Sales and Price
cor(Carseats$Price,Carseats$Sales)
```
The negative correlation coefficient suggests that sales decrease as prices increase. Its value of -0.4449507 suggests a weak correlation.

6. Added description and title in header. Included comments next to code.

7. Knitted output file to html.