---
title: "Assignment 3"
author: "Sean Bradford"
subtitle: 'Description: Construct and evaluate regression models using R to answer
  the assignment questions.'
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

1.
```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y
```

1a.
```{r}
plot(Y~X,xlab="X",ylab="Y",col="black")
```
The plot shows a linear relationship for Y based on X. As X increases, the values for Y increase as well. Based on this, we can fit a linear model to explain Y based on X.

1b.
```{r}
model1=lm(Y~X)
model1 #y=4.465 + 3.611X
summary(model1)
```
Equation that explains Y based on x: y = 4.465 + 3.611X.
Model accuracy is .6517 or 65%.

1c.
```{r}
sqrt(0.6517)
```
The square root of the coefficient of determination is equal to the correlation coefficient.

2.
```{r}
summary(mtcars)
```

2a.
James Prediction
```{r}
JModel=lm(mtcars$hp~mtcars$wt)
summary(JModel)
```
Chris Prediction
```{r}
CModel=lm(mtcars$hp~mtcars$mpg)
summary(CModel)
```
Chris's opinion is "right", compared to James's opinion. The accuracy of Chris's model is 0.6024, which is greater than the accuracy of James's model at 0.4339.

2b.
```{r}
hp_model=lm(hp~cyl+mpg,data=mtcars)
predict(hp_model,data.frame(cyl=4,
                            mpg=22))
```
The average estimated Horse Power of a car with 4 calendar and a mpg of 22 is 88.94.

3.
```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages('mlbench')
library(mlbench)
data(BostonHousing)
```

3a.
```{r}
Home_Value=lm(medv~crim+zn+ptratio+chas,data=BostonHousing)
summary(Home_Value)
```
This model is not accurate due to its Multiple R-squared (accuracy) of 0.3599.

3b. 

I. The house that bounds the Chas River is more expensive by a multiple of 4.58393. This is true because the coefficient of chas is 4.58393. If the other house costs $1000, then the identical house that bounds the Chas River would cost $4,583.93.

II. The house in the neighborhood with a pupil-teacher ratio of 15 is more expensive. This is true because the coefficient of ptratio is -1.49367, meaning that each increase of one unit in ptratio would decrease the house price by 1.49367. The value of the house with a ptratio of 15 decreases by (15x1493.67) $22,405.05. The value of the house with a ptratio of 18 decreases by (18x1493.67) $26,886.06. The house with a ptratio of 15 is more expensive by $4,481.01.

3c. Since the p-values of each coefficient are less than 0.05, we can say that each variable is statistically significant.

3d. 
```{r}
anova(Home_Value)
```
Order of importance ranked 1-4 (1 = most important, 4 = least important):
  1. crim
  2. ptratio
  3. zn
  4. chas
The larger the sum squared, the more importance given to the variable.
