---
title: "Assignment 2"
author: "Sean Bradford"
date: "June 29, 2022"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
subtitle: 'Description: This assignment involved using data transformation, data wrangling,
  and data exploration to answer different questions regarding the "Online Retail"
  dataset.'
---

Downloaded Online Retail dataset and assigned it to 'Retail' as a dataframe.
```{r}
Retail=read.csv("Mod4_Online_Retail (3).csv")
as.data.frame(Retail)
```

(1.)
```{r}
library(dplyr)
question1=Retail %>%
  group_by(Country) %>%
  summarise(txns=n(),pct=n()*100/nrow(Retail)) %>%
  filter(pct>1)

question1
```

(2.)
```{r}
Retail=Retail %>%
  mutate(TransactionValue=Quantity*UnitPrice)

summary(Retail) #ensuring variable was added to dataset
```

(3.)
```{r}
question3=Retail %>%
  group_by(Country) %>%
  summarise(totalsum=sum(TransactionValue)) %>%
  filter(totalsum > 130000)

question3
```

(4.)
```{r}
Temp=strptime(Retail$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
head(Temp)

Retail$New_Invoice_Date=as.Date(Temp)
Retail$New_Invoice_Date[20000]-Retail$New_Invoice_Date[10]

Retail$Invoice_Day_Week=weekdays(Retail$New_Invoice_Date)

Retail$New_Invoice_Hour=as.numeric(format(Temp,"%H"))

Retail$New_Invoice_Month=as.numeric(format(Temp,"%m"))
```
(4a.)
```{r}
FourA=summarise(group_by(Retail,Invoice_Day_Week),TransactionValue=n_distinct(InvoiceNo))
FourAa=mutate(FourA,transaction_percent=(TransactionValue/sum(TransactionValue))*100)
FourAa
```
(4b.)
```{r}
FourB=summarise(group_by(Retail,Invoice_Day_Week),Transaction_Volume=sum(TransactionValue))
FourBb=mutate(FourB,percentage=(Transaction_Volume/sum(Transaction_Volume))*100)
FourBb
```
(4c.)
```{r}
FourC=summarise(group_by(Retail,New_Invoice_Month),Transaction_Volume=sum(TransactionValue))
FourC=mutate(FourC,percentage=(Transaction_Volume/sum(Transaction_Volume))*100)
FourC
```
(4d.)
```{r}
Retail %>%
  filter(Country=='Australia') %>%
  group_by(New_Invoice_Date) %>%
  summarise(Max=max(TransactionValue))
```


(5.)
```{r}
germanygroup=Retail %>%
  group_by(Country) %>%
  filter(Country == 'Germany') %>%
  select(Country,TransactionValue)

hist(germanygroup$TransactionValue,
     main="Distribution of Transaction Values from Germany",
     xlab="Transaction Value",
     ylab="Number of Transactions",
     xlim=c(-600,900), #based on min and max
     breaks=100, #enhanced histogram readability
     col="blue",
     freq=TRUE)
```

(6.)
```{r}
Retailnaomit=na.omit(Retail) #removed NA's that were causing calculation errors

MostValCust=Retailnaomit %>%
  group_by(CustomerID) %>%
  summarise(sumtxns=sum(TransactionValue))

MostValCust[which.max(MostValCust$sumtxns),]
```

```{r}
RetTable=table(Retailnaomit$CustomerID)
RetTable=as.data.frame(RetTable)

HighestTxns=RetTable[which.max(RetTable$Freq),]

HighestTxns
```
Customer 17841 had the highest number of transactions at 7,983.
Customer 14646 had the highest total sum of transactions at 279,489.

(7.)
```{r}
missingvalues=colMeans(is.na(Retail)*100)

missingvalues
```

(8.)
```{r}
misscustid=Retail %>%
  filter(is.na(CustomerID)) %>%
  group_by(Country) %>%
  summarise(Missing_IDs=sum(is.na(CustomerID)))

misscustid
```
There were 135,080 total transactions with missing CustomerID records.


(10.)
```{r}
FranceCancel=Retail %>%
  group_by(Country) %>%
  filter(Country=='France') %>%
  filter(Quantity<0) %>%
  summarise(CancelledTxns=n())
# 149

FranceTxns=Retail %>%
  group_by(Country) %>%
  filter(Country=='France') %>%
  summarise(TotTxns=n())
# 8557

RR_French_Customers=149/8557
RR_French_Customers
```
The return rate for French customers is 0.017.

(11.)
```{r}
BestProduct=Retail %>%
  group_by(StockCode) %>%
  summarise(Revenue=sum(TransactionValue))

TheBestProduct=BestProduct[which.max(BestProduct$Revenue),]

TheBestProduct
```
Product "DOT" generated the highest revenue at $206,245.50.

(12.)
```{r}
UniqueCustomers=unique(Retail$CustomerID)

length(UniqueCustomers)
```
There are 4,373 unique customers in the dataset.
